Instructions for developing new pages for the MarineOmics webpage

### 2023-12-14 DRAFT_DNA_methylation.Rmd
added figure legend - meth ratio

```{r meth-bp, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/meth_ratio.png")
```

>>>>

```{r meth-ratio, echo = FALSE, out.width = "70%", fig.align = "center"}
knitr::include_graphics("DRAFT_DNA_methylation/meth_ratio.png")
```
_Frequency distribution of methylation ratios for CpG dinucleotides in oyster gill tissue._ DOI: [10.7717/peerj.215/fig-1](https://doi.org/10.7717/peerj.215/fig-1)
